Heuristics for the Score-Constrained Bin-Packing Problem

### 2018-01-15 paper/main.tex
updated main.tex

>>>>

The first heuristic to be dicussed is a first-fit decreasing heuristic, modified to account for the minimum total score width constraint. The strips are initially empty, thus we define a residual length $r(j)$ for each strip $S_j, j = 1, 2, ...$. The residual lengths are set equal to the strip lengths $l$, and reduce as boxes are added to the strips. Each strip $S_j$ that is packed with at least one
